MCMC convergence diagnostics

### 2023-01-14 src/naomi-simple_compare/comparison.Rmd
Clean up comparison report

@@

>>>>

```{r}
histogram_plot("beta_anc_rho")
```

@@

## Individual parameters

```{r}
ks_helper <- function(par) to_ks_df(par) %>% ks_plot(par = par)

ks_helper("beta")
ks_helper("logit")
ks_helper("log_sigma")

ks_helper("u_rho_x")
ks_helper("u_rho_xs")
ks_helper("us_rho_x")
ks_helper("us_rho_xs")
ks_helper("u_rho_a")
ks_helper("u_rho_as")

ks_helper("u_alpha_x")
ks_helper("u_alpha_xs")
ks_helper("us_alpha_x")
ks_helper("us_alpha_xs")
ks_helper("u_alpha_a")
ks_helper("u_alpha_as")
ks_helper("u_alpha_xa")

ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_alpha_x")
ks_helper("log_or_gamma")
```

## Summary table

```{r}
ks_summary <- lapply(unique(names(tmb$fit$obj$env$par)), function(x) {
  to_ks_df(x) %>%
    group_by(method) %>%
    summarise(ks = mean(ks), par = x)
}) %>%
  bind_rows() %>%
  pivot_wider(names_from = "method", values_from = "ks") %>%
  rename(
    "Parameter" = "par",
    "KS(aghq, tmbstan)" = "aghq",
    "KS(TMB, tmbstan)" = "TMB",
  )

ks_summary %>%
  gt::gt() %>%
  gt::fmt_number(
    columns = starts_with("KS"),
    decimals = 3
  )

ggplot(ks_summary, aes(x = `KS(TMB, tmbstan)`, y = `KS(aghq, tmbstan)`)) +
  geom_point(alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  labs(x = "KS(aghq, tmbstan)", y = "KS(TMB, tmbstan)") +
  theme_minimal()

ks_summary %>%
  mutate(`KS difference` = `KS(TMB, tmbstan)` - `KS(aghq, tmbstan)`) %>%
  ggplot(aes(x = `KS difference`)) +
    geom_boxplot(width = 0.5) +
    coord_flip() +
    labs(x = "KS(TMB, tmbstan) - KS(aghq, tmbstan)") +
    theme_minimal()
```
